I Compensate, therefore I Am \\ (accurate for DNN verification)

### 2024-01-23 Paper/proofs.tex
fix typos

			We want to show that $\mathrm{UB}(z) = \max (z)$ and $\mathrm{LB}(z) = \min (z)$ for the unique output nodes, and we will prove this for all $c\notin B_{zero}$ . As the MILP abstraction is a sound over-approximation, 
			it suffices to show that $\mathrm{UB}\leq \max (c)$ and $\mathrm{LB} \geq \min (c)$. We will prove this by induction on layers from the first hidden layer to the output layer. More specifically, we will prove the following lemmas:

>>>>

			We want to show that $\mathrm{UB}(z) = \max (z)$ and $\mathrm{LB}(z) = \min (z)$ for the unique output nodes. In fact, we will prove this for all $c\notin B_{zero}$ . As the MILP abstraction is a sound over-approximation, 
			it suffices to show that $\mathrm{UB}(c)\leq \max (c)$ and $\mathrm{LB}(c) \geq \min (c)$. We will prove this by induction on layers from the first hidden layer to the output layer. More specifically, we will prove the following lemmas:
